Rust Bug Fix Patterns

### 2022-09-20 methodology.tex
fixed fig labels

% TODO: tokens are not non terminals
% what do you mean about structs and enums?
% try to remove redundant content with respect to what is above
As mentioned above, we use Syn for parsing Rust. Syn handles all of Rust. Syn's nonterminals are primarily divided and implemented through two groups: Structs and Enums, which can be found on Syn webpage. The union of the item described in these two groups constitutes the list of our non terminals (\verb+NT+). The dimensions of our datapoints have been partly designed in a way that they adhere to the elements of \verb+NT+. The other part of our dimenstions is comprised of BC-related lexemes (\verb+BCL+), e.g. clone, Rc, Box, etc. The full list of \verb+BCL+ elements can be found within our artifact. We define dimension items as \verb+DI = NT+ $\cup$ \verb+BCL+, as this set also equals the columns of our tables.

@@

\begin{figure}[h]
\centering
\includegraphics[width=1\textwidth]{repos.png}
\label{f3}
\caption{Target Repositories}
\end{figure}

Now that we have set up our code analysis pipeline, we can start mining the Rust repositories. We target the top 18 most starred Rust projects on GitHub, at the time of data collection. The details of these projects are outlined in Table \ref{f3}. We computed the average code churn of the files within the projects. denoland/deno and swc-project/swc are the projects with largest number of LOCs and average code churn. Unsurprisingly, we captured a lot of instances from these two projects in our final clusters.

@@

\begin{algorithm}
\caption{An algorithm with caption}\label{alg}
\hspace*{2mm} \textbf{Input:} $R$ (target repositories)  \\
\hspace*{2mm} \textbf{Output:} $D_g$ (General code changes) \\
\hspace*{2mm} \textbf{Output:} $D_b$ (BC-related code changes)
\begin{algorithmic}
\State $D_g \leftarrow \phi$
\State $D_b \leftarrow \phi$
\For{$r \in R$}
    \For{$c \in \textsc{ExtractCommits}(r)$}
        \If{$c.msg$ contains bug fixing related keywords}
            \For{$\{f_b, f_a\} \in \textsc{GetModifiedRustFiles}(c)$}
                \For{$e \in \textsc{ASTDiff}(\textsc{Parse}(f_b), \textsc{Parse}(f_a))$}
                    \State $DP \leftarrow \textsc{GetDataPoint}(e)$
                    \State $DP \leftarrow c.hash \cup f_a.name \cup e.scope \cup DP $
                    \If{$\textsc{IsBCRelated}(e)$}
                        \State $DP \leftarrow \textsc{GetBCKeyword}(e) \cup DP $
                        \State $D_b \leftarrow D_b \cup DP$
                    \Else
                        \State $D_g \leftarrow D_g \cup DP$
                    \EndIf
                \EndFor
            \EndFor
        \EndIf
    \EndFor
\EndFor
\end{algorithmic}
\end{algorithm}

@@

There are two parameters that need tuning in DBSCAN. First parameter is $\epsilon$ which indicates a radius with which you can decide whether a point is a core point, a border point, or an outlier. Second parameter is the minimum number of point you would like each cluster to have. We denote his parameter with $Z$. We ran DBSCAN using different combinations of these two parameters. In Figure \ref{clustering}, we show nine different experiments with their respective parameter values. Within each subplot, the number of clustered points, noise points, and the number of clusters have been specified both for $D_g$ and $D_b$.

\begin{figure}[h]
\centering
\includegraphics[width=1\textwidth]{clusters.png}
\label{clustering}
\caption{Clustering Experiments}
\end{figure}

>>>>

As mentioned above, we use Syn for parsing Rust. Syn handles all of Rust. Syn's nonterminals are primarily divided and implemented through two groups: Structs and Enums, which can be found on Syn webpage. The union of the item described in these two groups constitutes the list of our non terminals (\verb+NT+). The dimensions of our datapoints have been partly designed in a way that they adhere to the elements of \verb+NT+. The other part of our dimenstions is comprised of BC-related lexemes (\verb+BCL+), e.g. clone, Rc, Box, etc. The full list of \verb+BCL+ elements can be found within our artifact. We define dimension items as \verb+DI = NT+ $\cup$ \verb+BCL+, as this set also equals the columns of our tables.

@@

\begin{figure}[h]
\centering
\includegraphics[width=1\textwidth]{repos.png}
\caption{\label{table:repos} Target Repositories}
\end{figure}

Now that we have set up our code analysis pipeline, we can start mining the Rust repositories. We target the top 18 most starred Rust projects on GitHub, at the time of data collection. The details of these projects are outlined in Table \ref{table:repos}. We computed the average code churn of the files within the projects. denoland/deno and swc-project/swc are the projects with largest number of LOCs and average code churn. Unsurprisingly, we captured a lot of instances from these two projects in our final clusters.

@@

\begin{algorithm}
\caption{\label{alg} Mining Algorithm}
\hspace*{2mm} \textbf{Input:} $R$ (target repositories)  \\
\hspace*{2mm} \textbf{Output:} $D_g$ (General code changes) \\
\hspace*{2mm} \textbf{Output:} $D_b$ (BC-related code changes)
\begin{algorithmic}
\State $D_g \leftarrow \phi$
\State $D_b \leftarrow \phi$
\For{$r \in R$}
    \For{$c \in \textsc{ExtractCommits}(r)$}
        \If{$c.msg$ contains bug fixing related keywords}
            \For{$\{f_b, f_a\} \in \textsc{GetModifiedRustFiles}(c)$}
                \For{$e \in \textsc{ASTDiff}(\textsc{Parse}(f_b), \textsc{Parse}(f_a))$}
                    \State $DP \leftarrow \textsc{GetDataPoint}(e)$
                    \State $DP \leftarrow c.hash \cup f_a.name \cup e.scope \cup DP $
                    \If{$\textsc{IsBCRelated}(e)$}
                        \State $DP \leftarrow \textsc{GetBCKeyword}(e) \cup DP $
                        \State $D_b \leftarrow D_b \cup DP$
                    \Else
                        \State $D_g \leftarrow D_g \cup DP$
                    \EndIf
                \EndFor
            \EndFor
        \EndIf
    \EndFor
\EndFor
\end{algorithmic}
\end{algorithm}

@@

There are two parameters that need tuning in DBSCAN. First parameter is $\epsilon$ which indicates a radius with which you can decide whether a point is a core point, a border point, or an outlier. Second parameter is the minimum number of point you would like each cluster to have. We denote his parameter with $Z$. We ran DBSCAN using different combinations of these two parameters. In Figure \ref{fig:clustering}, we show nine different experiments with their respective parameter values. Within each subplot, the number of clustered points, noise points, and the number of clusters have been specified both for $D_g$ and $D_b$.

\begin{figure}[h]
\centering
\includegraphics[width=1\textwidth]{clusters.png}
\caption{\label{fig:clustering} Clustering Experiments}
\end{figure}
